\section*{\Huge{Declaration}}
\vspace{1cm}
I hereby declare that this project is entirely my own work and that it has not been submitted as an exercise for a degree at this or any other university.

\vspace{1cm}
I have read and I understand the plagiarism provisions in the General Regulations of the University Calendar for the current year, found at \url{http://www.tcd.ie/calendar}.
\vspace{1cm}

I have also completed the Online Tutorial on avoiding plagiarism `Ready Steady Write', located at
\url{http://tcd-ie.libguides.com/plagiarism/ready-steady-write}.
\vspace{3cm}

Signed:~\rule{5cm}{0.3pt}\hfill Date:~\rule{5cm}{0.3pt}

\chapter*{Abstract}
A short summary of the problem investigated, the approach taken and the key findings. This should be around 400 words, or less.

This should be on a separate page.

DESCRIBE THE FOLLOWING LEARNING OUTCOMES (throughout the report, not the abstract)
\begin{enumerate}
	\item contribute to the design and development of systems at forefront of CS research and evaluate their performance
	\item apply theoretical knowledge to solve real world problems
	\item practice and further devel skills in comms, mgmt and teamwork
	\item practice and further develop skills in time management and reporting
	\item contribute to an ethical and profesional work culture
\end{enumerate}

\begin{enumerate}
	\item 
\end{enumerate}

\newpage
\onehalfspacing\raggedright %\raggedright turns off justification and hypenation

\section*{\Huge{Acknowledgements}}
Thanks Mum!

You should acknowledge any help that you have received (for example from technical staff), or input provided by, for example, a company.

\tableofcontents
\listoffigures
\listoftables
\newpage


\section*{\Huge{Nomenclature}}
\begin{tabular}{lp{9cm}l}
A&Area of the wing&$m^{2}$\\
B\\
C& Roman letters first, with capitals\ldots\\
a&then lower case.\\
b\\
c\\
$\Gamma$&Followed by Greek capitals\ldots\\
$\alpha$&then lower case greek symbols.\\
$\beta$\\
$\epsilon$\\
TLA&Finally, three letter acronyms and other abbreviations arranged alphabetically\\
\end{tabular}
\vspace{2cm}

If a parameter has a typical unit that is used throughout your report, then it should be included here on the right hand side.

If you have a very mathematical report, then you may wish to divide the nomenclature list into functions and variables, and then sub- and super-scripts.

Note that Roman mathematical symbols are typically in a serif font in italics.